\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-20 sections/methods.tex
Add: Synth data section to supplementary

  % TODO: Add reference: Karoline Faust, Franziska Bauchinger, Béatrice Laroche, Sophie de Buyl, Leo Lahti, Alex D Washburne, Didier Gonze, Stefanie Widder, "Signatures of ecological processes in microbial community time series", Microbiome (2018).
  The first method, hereby referred to as ``seqtime'', used generalized Lotka-Volterra (gLV) equations to model the microbial community dynamics and utilized the Klemm–Eguı́luz algorithm to generate a clique-based interaction network~\cite{Rottjers2018}.
  We used the \href{https://github.com/hallucigenia-sparsa/seqtime}{seqtime} R package to simulate communities with number of species ($N$) varying from 10 to 150 (10, 25, 50, 100, 150 and 200).
  The initial species concentrations are randomly sampled from a Poisson distribution and the simulation is rerun to generate a number of samples ($S$) varying from 50 to 500 (50, 100, 200, 500) for different communities.
  The abundance values of the species in the community at the end of the simulation time are used to create the OTU table.

>>>>

  The first method, hereby referred to as ``seqtime''~\cite{faustSignaturesEcologicalProcesses2018}, used generalized Lotka-Volterra (gLV) equations to model the microbial community dynamics and utilized the Klemm–Eguı́luz algorithm to generate a clique-based interaction network~\cite{Rottjers2018}.
  We used the \href{https://github.com/hallucigenia-sparsa/seqtime}{seqtime} R package to simulate communities with number of species ($N$) varying from 10 to 150 (10, 25, 50, 100, 150 and 200).
  The initial species concentrations are randomly sampled from a Poisson distribution and the simulation is rerun to generate a number of samples ($S$) varying from 50 to 500 (50, 100, 200, 500) for different communities.
  The abundance values of the species in the community at the end of the simulation time are used to create the OTU table.

### 2022-04-20 sections/supplementary.tex
Add: Synth data section to supplementary

    \subsubsection*{Data generation}
    Figures describing the original OTU tables or the interactions used to generate the community. Also include the seed and scripts for reproducing the networks.

    \subsubsection*{Processing using the \ac{micone} pipeline}

@@

>>>>

    \subsubsection*{Data generation}
    The synthetic interaction data for the study were generated using two methods.
    The first method, ``seqtime''~\cite{faustSignaturesEcologicalProcesses2018} utilized generalized Lotka-Volterra (gLV) equations to model the microbial community dynamics and made use of the Klemm–Eguı́luz algorithm to generate clique-based interaction networks~\cite{Rottjers2018}.
    We used the seqtime R package to simulate communities with different numbers of species and samples (see Methods for details).
    The second method, ``NorTA'' used the Normal to Anything (NorTA) approach coupled with a given interaction network topology to generate the abundance distribution of the microbial community~\cite{Kurtz2015}.
    We used the spieceasi R package to simulate communities with different abundance distributions and network topologies (see Methods for details).
    The scripts to generate these datasets can be found in the synthetic data and scripts repository (\href{https://github.com/segrelab/MiCoNE-synthetic-data}{https://github.com/segrelab/MiCoNE-synthetic-data})

    \subsubsection*{Processing using the \ac{micone} pipeline}
    The data was processed using the \ac{micone} pipeline using only the \ac{ni} step with the consensus networks as the final output.
    The configuration files (main.nf and nextflow.config) used to run the \ac{micone} pipeline as well the details of the pipeline execution (dag, report, timeline and trace) are in the "runs/norta" and "runs/seqtime" directories of the data and scripts repository (\href{https://github.com/segrelab/MiCoNE-pipeline-paper}{https://github.com/segrelab/MiCoNE-pipeline-paper})
    % TODO: Store pipeline results
    The results of the pipeline execution are stored on Zenodo[REF] at ...

@@

  \subsection*{Performance of network inference algorithms on seqtime data}
